Dear Thalmic Labs, 

My name is Daniel Johnson and I'm interested in working at Thalmic Labs in the role of Software Engineer - Product.  I'm excited by the prospect of working with new technology to measure the human body and motion and the applications for which it can be used.  As a graduate of the co-op program at the University of Waterloo, I believe I have the skills which would be needed to immediately begin contributing to the development of applications for the Myo at Thalmic Labs.  I am looking for work starting in January after finishing up my graduate work this fall.  

For the past two years, I've been a graduate student at the University of Waterloo building a 3-D simulation of the golf swing for use in designing golf clubs.  While this experience was research focused and the model was built using MapleSim and Matlab, I believe it provided me with the background knowledge in EMG, human motion capture (using IMUs and external cameras), and anthropometrics to quickly understand how the Myo interprets gestures. 

During my undergrad, I had many opportunities as part of the coop program at the University of Waterloo to design, develop, and distribute software.  At Apple Inc. (2 terms from 2010-2011) I designed and developed an internal application for testing location algorithms that included iOS, MacOS, and server-side components using Cocoa, Objective-C, and Python.  This application was selected from all of the intern projects to be presented to Senior Scott Forstall at the end of my time at Apple. While it was not intended to be released to the public, the application was included with internal builds of iOS and was constructed with a streamlined user experience in mind.  

My other co-op terms also gave me opportunities to design and develop software projects.  I spent 8 months working on statistics software for basketball coaches at CREZ where I worked mainly on developing the client-side of a platform for live-streaming basketball games. As the sole client developer, I fixed bugs, wrote new features using C\# and Visual Basic, delievered installer packages, and supported customers directly.  In my final work-term, I worked in VisualC++ building software used for identifying sea-ice in satellite imagery as part of the Vision and Image Processing Lab at UWaterloo.  At the same time, I supervised and assisted with the production of the lab website, built with Drupal, which was released as an open-source package.  

On my own, I've built a few smaller projects which can be found on my github profile at \url{http://github.com/proverbialsunrise}.  

I'm excited by the chance to work in a dynamic, goal-oriented work environment on a product that measures human motion.  I believe that Thalmic Labs would provide me with opportunities to thrive and I believe that I have some strong contributions to make to your product.  I look forward to hearing from you. 

