% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org

% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca

% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com

% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932

% (c) 2011 Daniel Johnson <d3johnso@uwaterloo.ca> 

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

\newlength{\outerbordwidth}

\pagestyle{empty}

\raggedbottom

\raggedright

\usepackage[svgnames]{xcolor}

\usepackage{framed}

\usepackage{tocloft}
\usepackage{hyperref}

%-----------------------------------------------------------

%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars

\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)

\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------

%Margin setup

\setlength{\evensidemargin}{-0.25in}

\setlength{\headheight}{-0.25in}

\setlength{\headsep}{0in}

\setlength{\oddsidemargin}{-0.25in}

\setlength{\paperheight}{11in}

\setlength{\paperwidth}{8.5in}

\setlength{\tabcolsep}{0in}

\setlength{\textheight}{9.75in}

\setlength{\textwidth}{7in}

\setlength{\topmargin}{-0.3in}

\setlength{\topskip}{0in}

\setlength{\voffset}{0.1in}

%-----------------------------------------------------------

%Custom commands

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]{\vspace{8pt}

  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}

    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}

    \end{shaded}

  }\vspace{-5pt}

}

\newcommand{\ressubheading}[4]{

\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}

		\textbf{#1} & #2 \\

		\textit{#3} & \textit{#4} \\

\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{\Large Daniel Johnson} & \textbf{\today} \\

Graduate Student, Systems Design Engineering, University of Waterloo & d3johnso@uwaterloo.ca \\

135 Moore Ave, Waterloo, ON, N2J1X4 \\

\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item {\bf Modeling:} 2-D and 3-D Dynamics, Simulation of mechanical systems, control systems

\item {\bf Development:} Objective-C/Cocoa, C/C++, Python, MATLAB, .NET and Visual Studio.

\item {\bf Robotics:} Autonomous Mapping, Computer Vision, Image processing.

\item Discovering and implementing new ideas. Give me a problem to solve and I'll find a way to solve it.

\item Communication: excels at writing clear and concise documents and presenting and explaining ideas.

\item Learning: loves to learn new things and explore new areas of research. 

\item Leadership: organizes and enables other workers to perform their tasks. Leads by example.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Research and Work Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item

	\ressubheading{University of Waterloo  (Vision and Image Processing Lab)}{Waterloo, ON}{Research Assistant}{May-Aug 2011}

	\begin{itemize}
	
		\resitem{Developed algorithms for processing SAR imagery of sea-ice in the Canadian North}
		\resitem{Implemented algorithms within existing image processing software in Visual C++.}
		\resitem{Gained knowledge of current computer vision algorithms and techniques}
    	\resitem{Supervised another student building a website for the lab}
	
	\end{itemize}

\item

	\ressubheading{Apple Inc.}{Cupertino, CA}{Software Engineering Intern - iOS Location Software}{Sep-Dec 2010 and Jan-Apr 2010}

	\begin{itemize}

	    \resitem{Designed and implemented a testing framework for location algorithms on iPhones and iPads.}
		\resitem{Improved location algorithms used in iOS.}
		\resitem{Developed internal mobile applications using Objective-C, C and C++ for iPhone.}

	\end{itemize}

\item 

	\ressubheading{Trimble Navigation}{Christchurch, NZ}{GPS Software Tester}{Summer 2009}

	\begin{itemize}

		\resitem{Tested hand held GPS devices for accuracy and interface.}
		\resitem{Developed and performed experiments on software keyboards for mobile devices.}
		\resitem{Established reliable methods for testing software on Windows Mobile.}

	\end{itemize}

\item

	\ressubheading{CREZ Basketball}{Waterloo, ON}{Software developer}{Sep 2007 - Dec 2007 and Jan 2007 - April 2007}

	\begin{itemize}

		\resitem{Developed software for basketball coaches in Visual Basic .NET and C\#}
		\resitem{Provided technical support through direct interaction with customers}
		\resitem{Created new features and fixed bugs in previous code.}

	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item

	\ressubheading{University of Waterloo}{Waterloo, ON}{BASc - Honours Systems Design Engineering, Co-operative Program}{2007 - 2012}
	
	\begin{itemize}

		\resitem{Graduated on Dean's Honour List with Distinction}

		\resitem{\emph{\textbf{SYDE 462/462}: Sep 2011-Apr 2012} - Developed location and mapping algorithms for the NASA Sample Retrieval Challenge.}

		\resitem{\emph{\textbf{SYDE 553/653} Sep 2011-Apr 2012} - 3-D Modeling and computer simulation of robotic soccer ball kicking leg for use in testing equipment.} 

		\resitem{\emph{\textbf{SYDE 362}: Jan-Apr 2011} - Designed and built a system for tracking energy use in homes including hardware sensors and software for aggregating and displaying data to homeowners and recommending alternative appliances.}
		
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Other Activities}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item \ressubheading{Hymnal Mobile Application}{Objective-C, C, Java }{Personal Programming Project}{2010}

  	\begin{itemize}

    	\resitem{Developed a mobile application for iPhone and Android to search and display hymns}
		\resitem{Negotiated with publisher for release of hymns in electronic form}
		\resitem{Unable to release due to copyright issues}

	\end{itemize}

\item \ressubheading{The Water Boys - UWaterloo Male A Cappella}{\url{www.waterboysuw.com}}{President}{2009-2012}

	\begin{itemize}
		\resitem{Interact with the community to plan gigs and organize events}
		\resitem{Rehearse weekly with a group of ~16 male singers}
		\resitem{Hold auditions for the group at the beginning of each term}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Awards}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\resitem {\emph{NSERC Alexander Graham Bell Scholarship} - Sep 2012}
	\resitem {\emph{NSERC Undergraduate Student Research Award} - May 2011}
	\resitem{\emph{President's Research Award} - Sep 2011}
	\resitem {\emph{NSERC Undergraduate Student Research Award} - Sep 2008}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Personal}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item {\bf Hobbies:} Singing (A Cappella and Barbershop in particular), Ultimate Frisbee, Soccer, Basketball, Squash

\item {\bf My Ideal Position:} Working with a team solving interesting problems related to 3-d dynamic modelling, biomechanics, and sports.  I'm passionate about playing sports competitively and getting involved in improving sports equipment or training would be fascinating. My Master's thesis is focused on the biomechanics of golf and I'd be excited to work on similar problems within other sports.

\end{itemize}

\end{document}

